---
title: "Creating reports for the users of Spöreg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{user-reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sporegr)
```

# Spöreg user reports overview

This vignette describes the Rmarkdown templates available in package sporegr.
It also describes suggested workflows on howto create a (possible) modified
report for a single user or to generate reports for all users in a single job.

The data to analyze must first be downloaded from ther central sporeg database
via the APEX interface (https://fd2.slu.se/ords/r/aqua/store100107/home)

## Available templates
After installation available templates can be listed:
```{r availabe_templates}
rmarkdown::available_templates(package = "sporegr")
```
# Single user report. Interactive
To create a report for a single user for a specific month you create a new .Rmd file
by going to "File / New File / R Markdown...", from the popup that appear choose "From template"
and then choose "Spöreg monthly user report (sporegr)".

Save this file in a directory where you have the APEX CSV-files downloaded. In the YAML-header of
the Rmd file find the "params" block and change "anvid", "year_no" and "month_no" to the desired
values. Finally format your report by clicking "Knit".


